### 2024-01-11 docs/projects/noj/ml.qmd
moved the noj docs

Residuals:
       Min          1Q      Median          3Q         Max
   -0.7887     -0.2280      0.0231      0.2356      0.8178

Coefficients:
                  Estimate Std. Error    t value   Pr(>|t|)
Intercept           2.2647     0.3103     7.2981     0.0000 ***
sepal-width         0.5371     0.0811     6.6238     0.0000 ***
petal-length        0.6748     0.0740     9.1169     0.0000 ***
petal-width        -0.4828     0.1607    -3.0046     0.0034 **
---------------------------------------------------------------------
Significance codes:  0 '***' 0.001 '**' 0.01 '*' 0.05 '.' 0.1 ' ' 1

Residual standard error: 0.3126 on 96 degrees of freedom
Multiple R-squared: 0.8617,    Adjusted R-squared: 0.8574
F-statistic: 199.4075 on 4 and 96 DF,  p-value: 4.187e-41

Equivalently, we may turn the model to a string and display that string as code:

<div class="sourceClojure">
```clojure
^kind/code
(-> evaluations
    flatten
    first
    :fit-ctx
    :model
    ml/thaw-model
    str)
```
</div>

<div class="sourceClojure">
```clojure
Linear Model:

Residuals:
       Min          1Q      Median          3Q         Max
   -0.7887     -0.2280      0.0231      0.2356      0.8178

Coefficients:
                  Estimate Std. Error    t value   Pr(>|t|)
Intercept           2.2647     0.3103     7.2981     0.0000 ***
sepal-width         0.5371     0.0811     6.6238     0.0000 ***
petal-length        0.6748     0.0740     9.1169     0.0000 ***
petal-width        -0.4828     0.1607    -3.0046     0.0034 **
---------------------------------------------------------------------
Significance codes:  0 '***' 0.001 '**' 0.01 '*' 0.05 '.' 0.1 ' ' 1

Residual standard error: 0.3126 on 96 degrees of freedom
Multiple R-squared: 0.8617,    Adjusted R-squared: 0.8574
F-statistic: 199.4075 on 4 and 96 DF,  p-value: 4.187e-41

@@

<div><pre><small><small>source: <a href="https://github.com/scicloj/clojure-data-scrapbook/blob/main/projects/main/noj/notebooks/ml.clj">projects/main/noj/notebooks/ml.clj</a></small></small></pre></div>

>>>>

Residuals:
       Min          1Q      Median          3Q         Max
   -0.7698     -0.2528      0.0188      0.2103      0.5987

Coefficients:
                  Estimate Std. Error    t value   Pr(>|t|)
Intercept           1.8690     0.2997     6.2352     0.0000 ***
sepal-width         0.6645     0.0791     8.3956     0.0000 ***
petal-length        0.7226     0.0722    10.0028     0.0000 ***
petal-width        -0.6541     0.1594    -4.1043     0.0001 ***
---------------------------------------------------------------------
Significance codes:  0 '***' 0.001 '**' 0.01 '*' 0.05 '.' 0.1 ' ' 1

Residual standard error: 0.3154 on 96 degrees of freedom
Multiple R-squared: 0.8466,    Adjusted R-squared: 0.8418
F-statistic: 176.6175 on 4 and 96 DF,  p-value: 6.018e-39

@@

<div><pre><small><small>source: <a href="https://github.com/scicloj/clojure-data-scrapbook/blob/main/projects/noj/notebooks/ml.clj">projects/noj/notebooks/ml.clj</a></small></small></pre></div>
